
%  next 2 lines pull in the NASA.cls file, put options between []
\documentclass[]             % options: RDPonly, coveronly, nocover
{aiaa-tc}                       %   plus standard article class options

%  Fill in the following catagories between the braces {}
\title{Open-Source Conceptual Sizing Models for the Hyperloop Passenger Pod}

\author{
  Jeffrey C. Chin%
     \footnote{Aerospace Engineer, Propulsion Systems Analysis Branch, Mail Stop 5-10, AIAA Member},
  \ Justin S. Gray\footnotemark[\value{footnote}] ,%
     %\thanks{Aerospace Engineer, MDAO Branch, Mail Stop 5-10, AIAA Member}
  \ Scott M. Jones\footnotemark[\value{footnote}] ,%
     %\thanks{Aerospace Engineer, MDAO Branch, Mail Stop 5-10, AIAA Member}
  \ Jeffrey J. Berton\footnotemark[\value{footnote}]%
    %\thanks{Aerospace Engineer, MDAO Branch, Mail Stop 5-10, AIAA Member}
   \\
  {\normalsize\itshape
  NASA Glenn Research Center, Cleveland, OH}
}

% Define commands to assure consistent treatment throughout document
\newcommand{\eqnref}[1]{(\ref{#1})}
\newcommand{\class}[1]{\texttt{#1}}
\newcommand{\package}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{#1}}
\newcommand{\BibTeX}{\textsc{Bib}\TeX}

\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{0pt}

\usepackage{minted} %syntax highlighting
\usepackage{color} %syntax highlighting
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{amsmath} %math equations
\usepackage{subfiles} %break up document into subfiles
\usepackage{hyperref} %hyperlinks
\usepackage{courier} %courier font for variable names
\usepackage{cleveref} %section references
\usepackage[all]{hypcap} %figure references point to top of figure (must come after hyperref)
\usepackage{nomencl} %nomenclature
\usepackage{subfiles} %split sections into separate docs

\usepackage{setspace} %Pro­vides sup­port for set­ting the spac­ing be­tween lines in a doc­u­ment
\usepackage{wrapfig} %Al­lows fig­ures or ta­bles to have text wrapped around them.
\usepackage{caption} %The cap­tion pack­age pro­vides many ways to cus­tomise the cap­tions in float­ing en­vi­ron­ments like fig­ure and ta­ble
\usepackage{lscape} %Mod­i­fies the mar­gins and ro­tates the page con­tents but not the page num­ber.
\usepackage{appendix}
\usepackage{listings} %Code
\usepackage[section]{placeins} %De­fines a \FloatBar­rier com­mand, be­yond which floats may not pass; 
\usepackage[superscript]{cite} %The pack­age sup­ports com­pressed, sorted lists of nu­mer­i­cal ci­ta­tions
\usepackage{esdiff} %The pack­age makes writ­ing deriva­tives very easy.
\usepackage{bm} %The bm pack­age de­fines a com­mand \bm which makes its ar­gu­ment bold. (math)
\usepackage{tabulary} %wider table
\usepackage{gensymb} %degree symbol
\usepackage{booktabs} % en­hances the qual­ity of ta­bles

\lstset{frame=single}
\newcommand{\txt}{\textrm}

\newcommand{\cent}{{\mathrm{c}\mkern-6.5mu{\mid}}}

\captionsetup[figure]{margin=5pt,font=small,labelfont=bf,textfont=bf,justification=justified,}
%\captionsetup[wrapfigure]{margin=5pt,font=small,labelfont=bf,justification=justified,singlelinecheck=off}
\captionsetup[table]{margin=5pt,font=small,labelfont=bf,textfont=bf,justification=justified,position=top}

\bibliographystyle{aiaa}

\usepackage{lettrine} %The let­trine pack­age sup­ports var­i­ous dropped cap­i­tals styles
\usepackage{verbatim} %reimplements verbatim, block comments

%nomenclature
\makenomenclature
\usepackage{multicol}
\makeatletter
\@ifundefined{chapter}
  {\def\wilh@nomsection{section}}
  {\def\wilh@nomsection{chapter}}


%\def\thenomenclature{%
%  \begin{multicols}{2}[% 2 column layout
%    \csname\wilh@nomsection\endcsname*{\nomname}
%    \if@intoc\addcontentsline{toc}{\wilh@nomsection}{\nomname}\fi
%    \nompreamble]
%  \list{}{%
%    \labelwidth\nom@tempdim
%    \leftmargin\leftmargini
%    \advance\leftmargin\leftmargini
%    \itemsep\nomitemsep
%    \let\makelabel\nomlabel}%
%}
%\def\endthenomenclature{%
%  \endlist
%  \end{multicols}
%  \nompostamble}
%\makeatother

%these seemed to be necessary with minted... not sure what they do..
\makeatletter
\color{black}
\let\default@color\current@color
\makeatother

%reference appendix
\crefname{appsec}{Appendix}{Appendices}
\begin{document}

\maketitle

\begin{abstract}
Hyperloop is a new transportation concept proposed as a faster, cheaper alternative to California's high speed rail project.
It consists of a passenger pod traveling through a tube under light vacuum and suspended on air bearings.
Although the original proposal looks promising,
it assumes tube and pod dimensions are independently sizable without fully acknowledging
the constraints of the vehicle compressors and pod geometry.
Using open-source toolsets a new sizing method is developed, focusing on 
the strong thermodynamic interactions between the two largest systems: the tube and the pod.
These additional considerations require doubling the originally considered tube diameter
and limit the maximum pod speed to about 620 mph.
Although larger and slightly slower than originally intended, the estimated travel time only increases by five minutes,
so the overall performance is not dramatically affected.
In addition, the proposed on-board heat exchangers are not an ideal solution
to achieve reasonable equilibrium air temperatures within the tube.
Removal of this subsystem represents a potential reduction in weight, energy, and complexity of the pod.
In light of these finding, the core concept remains a compelling possibility,
although additional engineering and economic analyses are markedly necessary before a more complete design can be developed.
\\
\\
\\
\\

\end{abstract}  

\setcounter{secnumdepth}{1}
\setcounter{tocdepth}{1}
%\tableofcontents
%\listoffigures
%\listoftables
\printnomenclature
 
\subfile{hyperloop}

\bibliographystyle{unsrt} %sorted by appearence, consider using natbib?
\bibliography{bibliography}

%\subfile{appendix}

\end{document}